\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin=1.7cm]{geometry}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*,itemsep=2pt,topsep=3pt}

\newcommand{\sectionspacebefore}{1.05em}
\newcommand{\sectionspacetoline}{-0.12em}
\newcommand{\sectionspacetocontent}{0.58em}
\newcommand{\roleblockgap}{0.65em}

\newcommand{\cvsection}[1]{
  \par\vspace{\sectionspacebefore}
  {\large\bfseries\color{black}#1}\par
  \vspace{\sectionspacetoline}
  \noindent\rule{\textwidth}{0.45pt}\par
  \vspace{\sectionspacetocontent}
}

\newcommand{\cvname}{Matthias Hutter}
\newcommand{\cvtitle}{Senior Software Architect | Platform and Financial Data Systems}
\newcommand{\cvlocation}{Vienna, Austria}
\newcommand{\cvphone}{+43 650 8223546}
\newcommand{\cvemail}{hutter.matthias@gmail.com}
\newcommand{\cvgithub}{github.com/ScepticMatt}
\newcommand{\cvlinkedin}{linkedin.com/in/matthias-hutter-7837349a}

\newcommand{\role}[4]{
  \textbf{#1} \hfill #2\\
  \textit{#3} \hfill \textit{#4}
  \vspace{0.25em}
}

\begin{document}

{\LARGE\textbf{\cvname}}\\[0.15em]
{\large\cvtitle}\\[0.45em]
{\small \cvlocation{} \textbar{} \cvphone{} \textbar{} \href{mailto:\cvemail}{\cvemail}}\\
{\small \href{https://\cvgithub}{\cvgithub} \textbar{} \href{https://\cvlinkedin}{\cvlinkedin}}

\cvsection{Professional Summary}
\begin{itemize}
  \item Senior Software Architect and Infrastructure Leader with 8+ years delivering backend, platform, and data systems in fintech and digital assets.
  \item End-to-end ownership across architecture, implementation, CI/CD, observability, incident response, and production operations.
  \item Proven delivery of audit-ready financial data pipelines and reporting used by trading, operations, and finance stakeholders.
  \item Hands-on technical leader with experience hiring, mentoring, and scaling engineering teams in distributed and cross-functional environments.
\end{itemize}

\cvsection{Work Experience}
\role{Director of Infrastructure}{Jan 2023 -- Present}{Dark Forest Limited}{Vienna / Remote}
\begin{itemize}
  \item Own infrastructure architecture and operations for a regulated electronic trading environment, including multi-cloud and bare-metal deployments.
  \item Built and operated validator infrastructure across \textasciitilde20 PoS networks (\textasciitilde60 validators), with strong reliability and operational discipline.
  \item Designed and delivered the Accounting Data Manager (ADM), consolidating 10 exchange feeds and internal metadata into auditable golden-source datasets.
  \item Implemented automated NAV, balance, and PnL reporting across API, dashboard, email, Slack, and Excel workflows used in daily operations.
  \item Partnered with engineering, trading, operations, and finance stakeholders in a distributed setup to align delivery priorities and incident response.
\end{itemize}
\textbf{Tech:} Node.js, TypeScript, OpenAPI, PostgreSQL, kdb+, AWS, OVH, React, Keycloak, Terraform, Ansible

\vspace{\roleblockgap}
\role{Crypto Research Director}{Jan 2022 -- Dec 2022}{Dark Forest GmbH}{Vienna}
\begin{itemize}
  \item Led infrastructure architecture and automation during the company build-out phase for trading and staking workloads.
  \item Automated provisioning and configuration management for dedicated hardware and cloud hosts.
  \item Built internal services for blockchain and market data ingestion to support trading decisions and reporting workflows.
\end{itemize}
\textbf{Tech:} Python, Java, Spring, Terraform, Ansible, Kafka, RabbitMQ, Prometheus, React

\vspace{\roleblockgap}
\role{Lead Technical Architect}{Mar 2020 -- Dec 2022}{Kivu Technologies}{Vienna}
\begin{itemize}
  \item Led modernization of legacy systems toward bi-temporal time-series graph processing architecture.
  \item Designed temporal graph components and automated data processing pipelines for enterprise integration use cases.
  \item Drove delivery across product, engineering, QA, and customer stakeholders from requirements through implementation, acceptance testing, and production support.
\end{itemize}
\textbf{Tech:} Java, Vert.x, Spring, Lucene, RocksDB, PostgreSQL, MySQL, Jenkins

\vspace{\roleblockgap}
\role{Backend Team Lead}{Nov 2018 -- Mar 2020}{Kivu Technologies}{Vienna}
\begin{itemize}
  \item Managed backend roadmap, sprint delivery, and engineering standards for core platform services.
  \item Hired and mentored backend engineers through structured onboarding, code review, and technical coaching.
  \item Improved development workflows through stronger CI practices, quality gates, and clearer definition-of-done criteria.
\end{itemize}

\vspace{\roleblockgap}
\role{Backend Developer}{Sep 2017 -- Nov 2018}{Kivu Technologies}{Vienna}
\begin{itemize}
  \item Built backend APIs and integration layers between frontend applications and core graph services.
  \item Developed Redis-based metadata storage using Java APIs, Lua scripts, and C-module integrations.
  \item Helped align frontend and backend teams through coordinated refactoring and delivery planning.
\end{itemize}

\vspace{\roleblockgap}
\role{University Tutor (Computer Science)}{Jan 2016 -- Mar 2017}{URACCAN}{Nicaragua}
\begin{itemize}
  \item Taught algorithms, complexity basics, and applied programming in C.
  \item Coached trainee teachers and supported curriculum delivery in intercultural education programs.
\end{itemize}

\cvsection{Technical Skills}
\textbf{Core Areas:} Platform Architecture, Backend Engineering, Financial Data Systems, Infrastructure Automation, Team Leadership\\
\textbf{Languages:} TypeScript, Java, Python, C/C++, JavaScript, SQL\\
\textbf{Backend and APIs:} Node.js, Express, Vert.x, Spring, REST, OpenAPI, RabbitMQ, Kafka\\
\textbf{Data and Storage:} PostgreSQL, MySQL, Redis, RocksDB, Apache Lucene, kdb+\\
\textbf{Cloud and DevOps:} AWS, Linux, Terraform, Ansible, Docker, CI/CD, GitHub Actions\\
\textbf{Observability and Identity:} Prometheus, Alertmanager, Grafana, OIDC, RBAC, Keycloak

\cvsection{Education}
\textbf{Coursework in Electronics Engineering} \hfill 2011 -- 2014\\
Swiss Federal Institute of Technology (ETH Zurich)

\vspace{0.35em}
\textbf{Coursework in Physics} \hfill 2008 -- 2011\\
Swiss Federal Institute of Technology (ETH Zurich)

\vspace{0.35em}
\textbf{Electrical Engineering Apprenticeship + Secondary School Diploma} \hfill 2003 -- 2008\\
Werkschulheim Felbertal

\end{document}
